%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{hyperref}
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf \href{https://neurolife77.github.io/}{Dominic Boutet}} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
%\moveleft.5\hoffset\centerline{625 Milton Sreet} % Your address
\moveleft.5\hoffset\centerline{Montreal, Qc, Canada}
\moveleft.5\hoffset\centerline{(438) 390-3895}
\moveleft.5\hoffset\centerline{dominic.boutet@mail.mcgill.ca}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{OBJECTIVES}  

Investigating the neurophysiological mechanisms of brain activity in health and diseases through computational modelling and AI/ML approaches.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

%{\sl Diploma of College studies} \\
%Cégep Régional de Lanaudière à l'Assomption, Qc, CA, completed May 2020 \\
%Concentration: Natural Sciences \\
%\\%*[0.25cm]
{\sl Bachelor of Science,} Interdisciplinary Science \\
McGill University, Qc, CA, expected May 2023 \\
Concentration: Neuroscience (Major) \& Computer Science (Minor) 
\\Current cGPA: 3.97

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{RESEARCH EXPERIENCE}

{\sl Research internship} \hfill May 2021-Now\\The Neuro at \href{https://www.neurospeed-bailletlab.org/}{NeuroSPEED-BailletLab}, Qc, CA\\*[0.25cm] 
%
Summer research project (2021):
\vspace*{0.15cm}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Literature review of multi-scale modelling approaches with a focus on The Virtual Brain (\href{https://www.thevirtualbrain.org/tvb/zwei}{TVB}), and of model calibration approaches for dynamical models.
\item Implementation of a simulation workflow and testing of the different calibration approaches for a TVB model with magnetoencephalography (MEG) data.
\end{itemize}
\vspace{-0.10cm}

\href{https://www.nserc-crsng.gc.ca/students-etudiants/ug-pc/usra-brpc_eng.asp}{NSERC USRA} summer project (2022):
\vspace*{0.15cm}
\begin{itemize} \itemsep -2pt % Reduce space between items
	\item Design and implementation of a novel parameter space reduction algorithm that guides search-based optimization algorithms in high-dimensional space.
	\item Writing the API for neural networks and other components of the algorithm.
	\item Implementation of accelerated simulator neurons and neural mass models.
	\item Implementation of various search algorithms for performance testing.
	\item Writing of a manuscript reporting the algorithm and its performance.
\end{itemize}

\section{VOLUNTEER EXPERIENCE}

{\sl Undergraduate Research Lead} \hfill January 2022-July 2022\\ \href{https://yourekacanada.org/}{Youreka Canada}, CA\\*[0.25cm] 
Youreka project:
\vspace*{0.15cm}
\begin{itemize} \itemsep -2pt % Reduce space between items
	\item Acting as PI for a research project with a team of 3 high school students.
	\item We established a proof of concept for COVID-19 case forecasting using time series linear regression on vaccination data from daily US updates.
	\item We wrote a manuscript reporting our results, prepared a poster and performed a presentation at the Regionals. We won and also presented at the Nationals.
\end{itemize}

\section{RELEVANT SKILLS}
Computer skills:
\vspace*{0.15cm}
\begin{itemize}
	%\item Extensive experience with the use of Python in a research setting.
	\item Extensive experience with relevant libraries such as \href{https://numpy.org/doc/stable/index.html}{numpy}, \href{https://pytorch.org/}{pytorch}, etc.
	\item Significant experience interacting with open source projects. %such as TVB-library and the simulation-based inference (SBI) toolkit.
	\item Significant knowledge of AI/ML models and optimization algorithms.
\end{itemize}
\vspace{-0.10cm}
General skills:
\vspace*{0.15cm}
\begin{itemize}
	\item Great creative problem solving capacities and autonomy.
	\item Great communication and teaching abilities in official and non-official settings.
	\item Good leadership abilities in a research or problem solving setting.
\end{itemize} 

%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

%\section{EXTRA-CURRICULAR \\ ACTIVITIES} 

%Elected {\it House Manager}, Rho Phi Sorority \\
%Elected {\it Sports Chairman} \\
%Attended Krannet Leadership Conference \\
%Headed delegation to Rho Phi Congress \\
%Junior varsity basketball team \\
%Participant, seven intramural athletic teams 

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}